Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
fixing brian rounding errors

Based on our numerical results (\ref{sec:numerical}) and the work of \citet{McCourt+12}) we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
  cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius.  This condition translates into a
critical minimum heating rate
\begin{align}
v_{w} > v_{\rm TI} \simeq
  {\rm max}\begin{cases}
   200 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
   200 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
\approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
  \end{cases}
  \label{eq:cooling3}
\end{align}
where the final condition corresponds to the low wind heating limit ($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our numerical and analytic results show that the stagnation radius moves out to the break radius $r_b$; the quasi-hydrostatic structure that develops in this case greatly increases the gas density, resulting in thermal instability.

The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
\begin{align}
\frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq
  {\rm min}\begin{cases}
   5\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
3\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.38} &, \text{core}, \zeta < \zeta_c \\
   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
2.5\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
where the first line for each case is derived using equation
(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
the second line corresponds to the low wind heating limit $\zeta \ll \zeta_c$.  $\zeta_c$ is
calculated using the empirical correlation for core galaxies
$r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{0.2}$ which follows from
equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$ correlation derived from the results of \citet{LauerFaber+:2007a}.  {\bf BDM: check this}

@@

%For these highest mass
%black holes, the maximum accretion rate as set by the SN Ia
%radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could instead cap the
%accretion rate close to the thermally-unstable value (see discussion following eq.~[\ref{eq:eddr_Ia}]).  For lower mass black holes, the maximum accretion rate set by SNe Ia is significantly higher and cannot
%also prevent the development of thermally unstable flows,
%i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm TI}$.

@@

%However, it is important to note that the
 %   inflow rate on large scales (which we calculate) may differ from
  %  the actual accretion rate as outflows could occur on small
   % scales. The outflow rate would depend on the angular momentum of
    %the infalling gas and thus the angular momentum of stars in the
    %nucleus. The in turn would vary systematically with $\Mbh$.

>>>>

Based on our numerical results (\ref{sec:numerical}) and the work of \citet{McCourt+12}) we define thermally stable flows according to the criterion $\dot{q}_{\rm heat} > 10|\dot{q}_{\rm rad}|$ ($t_{\rm
  cool} > 10t_{\rm ff}$) being satisfied near the stagnation radius.  This condition translates into a
critical minimum heating rate
\begin{align}
v_{w} > v_{\rm TI} \simeq
  {\rm max}\begin{cases}
   300 \eta_{0.02}^{0.14} M_{\bullet,8}^{0.11}\,{\rm km\,s^{-1}}  &, \text{core}\\
   260 \eta_{0.02}^{0.17} M_{\bullet,8}^{0.08}\,{\rm km\,s^{-1}}   &, \text{cusp}  \\
\approx \sigma_0(r_{b}/r_{\rm soi})^{0.5(1-\Gamma)} &, \zeta \ll \zeta_c, 
  \end{cases}
  \label{eq:cooling3}
\end{align}
where the final condition corresponds to the low wind heating limit
($\zeta \ll \zeta_c$; eq.~[\ref{eq:zetacrit}]), for which our
numerical and analytic results show that the stagnation radius moves
out to the break radius $r_b$; the quasi-hydrostatic structure that
develops in this case greatly increases the gas density, resulting in
thermal instability.

The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
\begin{align}
  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq {\rm
    min}\begin{cases}
    2\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
    7\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
    1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
where the first line for each case is derived using equation
(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, whereas
the second line corresponds to the low wind heating limit $\zeta \ll
\zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
core galaxies $r_{b}/r_{\rm soi} \approx 7.6M_{\bullet,8}^{-0.2}$ {\bf
AG: this is the second time I have caught this, is there any
particular reason you think this should be +0.2 not -0.2} which
follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
correlation derived from the results of \citet{LauerFaber+:2007a}.
{\bf BDM: check this}

@@

% For these highest mass black holes, the maximum accretion rate as
% set by the SN Ia radius (green lines; eq.~[\ref{eq:eddr_Ia}]) could
% instead cap the accretion rate close to the thermally-unstable value
% (see discussion following eq.~[\ref{eq:eddr_Ia}]).  For lower mass
% black holes, the maximum accretion rate set by SNe Ia is
% significantly higher and cannot also prevent the development of
% thermally unstable flows, i.e. $\dot{M}_{\rm Ia} \gg \dot{M}_{\rm
% TI}$.

@@

    % However, it is important to note that the inflow rate on large
    % scales (which we calculate) may differ from
    % the actual accretion rate as outflows could occur on small
    % scales. The outflow rate would depend on the angular momentum of
    % the infalling gas and thus the angular momentum of stars in the
    % nucleus. The in turn would vary systematically with $\Mbh$.
